State of the Practice of Lattice Boltzmann Method Software Development

### 2021-05-19 StateOfPractice/Peter-Notes/Report/Report.tex
added notes on artifacts present

\documentclass[12pt, notitlepage]{article}
\usepackage{amsmath, mathtools}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{titling}
\usepackage{blindtext}
\usepackage{indentfirst}

@@

>>>>

\documentclass[12pt, notitlepage]{article}
\usepackage{amsmath, mathtools}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{titling}
\usepackage{blindtext}
\usepackage{multicol}
\usepackage{indentfirst}

@@

split into common (16-23), less common (8-15), rare artifacts (0-7) lists

in each split section comment on why almost always present are there and do the best ranked have the common/rare artifacts?, if so comment on how they could have contribted to higher rankings in specific quality AHP rankings

Common (16-23):
\begin{singlespace}
\begin{multicols}{2}	
\begin{itemize}
	\item License 
	\item Makefile / Build File 
	\item README File 
	\item Tutorial 
	\item List of Related Articles / Publications 
	\item Dependency Notes 
	\item Requirements Specification / Theory Notes
	\item Authors / Developers
	\item Installation Guide/Instructions 
	\item Bug Tracker
\end{itemize}
\end{multicols}
\end{singlespace}

Less Common (8-15):
\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item User Manual/Guide
			\item Version Control
			\item Change Log / Release Notes
			\item Functional Specification/Notes
			\item Design Documentation
			\item Performance Information/Notes
			\item Test Plan/Report/Script/Data/Cases
		\end{itemize}
	\end{multicols}
\end{singlespace}

Rare (1-7):
\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item Developer/Contributing Manual/Guide
			\item Video Guide (including YouTube)
			\item API Documentation
			\item Verification and Validation Plan/Notes
			\item FAQ / Forum
		\end{itemize}
	\end{multicols}
\end{singlespace}
